---
title: "R Notebook"
output: html_notebook
---
Task 1.
Load the data again, clean_names(), and re-familiarise yourself with it
```{r}
library(tidyverse)
library(janitor)
library(fastGraph)
library(infer)
```
```{r}
house_sales <- read_csv("data/ames.csv") %>%
  clean_names()

range(house_sales$lot_area) # to check what the min and the max value are to identify possible outliers
```

Task 2.
Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
house_sales %>%
  ggplot(aes(x = lot_area)) +
  geom_histogram(col = "black", fill = "steel blue", alpha = 0.7)+
  # to make sure all the data is visualised and can be seen on the graph
  coord_cartesian(xlim = c(1000, 220000)) 

# the data is highly skewed
```

Task 3.
Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
bootstrap_house_sales <- house_sales%>%
  rep_sample_n(size = 2930, replace = TRUE, reps = 100) %>%
  summarise(
    mean_lot_area = mean(lot_area)
  )
```

```{r}
lot_plot_boot <- bootstrap_house_sales %>%
  ggplot(aes(x = mean_lot_area)) +
  geom_histogram(col = "white", fill = "steel blue", alpha = 0.7)
  )
```
Task 4.
Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution

```{r}
ci_95 <- bootstrap_house_sales %>%
  summarise(
    mean = mean(mean_lot_area),
    lower_bound = quantile(mean_lot_area, probs = 0.025),
    upper_bound = quantile(mean_lot_area, probs = 0.975)
  )
```
```{r}
infer_ci_95 <- bootstrap_house_sales %>%
  get_confidence_interval(level = 0.95, type = "percentile")
```
```{r}
bootstrap_sample <- house_sales %>%
  specify(response = lot_area) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```

```{r}
bootstrap_sample %>%
  visualise() +
  shade_confidence_interval(endpoints = infer_ci_95)
```

Task 5.
You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?

```{r}
ci_99 <- bootstrap_house_sales%>%
  summarise(
    mean = mean(mean_lot_area),
    lower_bound = quantile(mean_lot_area, probs = 0.005),
    upper_bound = quantile(mean_lot_area, probs = 0.995)
  )
```

```{r}
infer_ci_99 <- bootstrap_house_sales %>%
  get_confidence_interval(level = 0.99, type = "percentile")

bootstrap_sample %>%
  visualise() +
  shade_confidence_interval(endpoints = infer_ci_99)
```

Task 6.
Calculate the point estimate of the mean(lot_area)

