---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
data(msleep)
```

```{r}
msleep
```
H0: there's no difference between the mean sleep_total in the sampled population of animal types and the typical value for jabberwockies.
HA: the mean sleep_total of the sampled population is significantly higher than the typical value for jabberwokies.

å = 0.05

```{r}
obs_stat <- msleep %>%
  summarise(mean_sleep_total = mean(sleep_total), na.rm = TRUE) 
```

Average sleep_total is __10.43__ hours

```{r}
msleep %>%
  ggplot(aes(x = sleep_total))+
  geom_histogram(col = "white") 
  #geom_boxplot()
```

```{r}
library(infer)

sample_300 <- msleep %>%
  rep_sample_n(size = 83, reps = 300)
```
```{r}
obs_stat <- sample_300 %>%
  ungroup() %>%
  summarise(
    mean_sleep_total = mean(sleep_total))
```

```{r}
null_dist <- msleep %>%
  specify(response = sleep_total) %>%
  hypothesise(null = "point", mu = 7) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")
```
```{r}
null_dist %>%
  visualise(bins = 30) +
  shade_p_value(obs_stat = obs_stat$mean_sleep_total, direction = "right")
```

```{r}
p_value <- null_dist %>%
  get_p_value(obs_stat = obs_stat$mean_sleep_total, direction = "right")
```

Question 3.
Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

```{r}
msleep %>%
  filter(!is.na(vore)) %>%
  group_by(vore)%>%
  summarise(mean_sleep = mean(sleep_total))
```
H0: omnivore sleep for as long as herbivores on average (μ1 − μ2 = 0)
HA: omnivores sleep for significantly longer than herbivores (Ha: μ0 > μ2)

```{r}
msleep_vore <- msleep %>%
  filter(!is.na(vore)) %>%
  filter(vore == "herbi" | vore == "omni")
 
```

```{r}
msleep_vore %>%
  group_by(vore) %>%
  mutate(mean_sleep_t = mean(sleep_total)) %>%
  ggplot(aes(x = sleep_total, y = vore)) +
  geom_boxplot()
```
```{r}
msleep_vore_two <- msleep_vore %>%
  select(vore, sleep_total)%>%
  group_by(vore) %>%
  slice(1:5)
```



```{r}
null_distribution <- msleep_vore_two %>% 
  specify(sleep_total ~ vore) %>% 
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))
```
```{r}
obser_stat <- msleep_vore_two%>%
  specify(sleep_total ~ vore) %>%
  calculate(stat = "diff in means", order = c("omni", "herbi"))
```
```{r}
null_distribution %>%
  visualize()+
  shade_p_value(obs_stat = obser_stat, direction = "both")
```

```{r}
null_distribution %>%
  get_p_value(obs_stat = obser_stat, direction = "both")
```
Question 4. 
Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.

```{r}
msleep_dom <- msleep %>%
  filter(!is.na(conservation))%>%
  mutate(is_domesticated = ifelse(conservation == "domesticated", TRUE, FALSE))
```
```{r}
null_d <- msleep_dom %>%
  specify(response = is_domesticated, success = "TRUE") %>% 
  hypothesize(null = "point", p = 0.05) %>% 
  generate(reps = 10000, type = "draw") %>% 
  calculate(stat = "prop")
```
```{r}
null_d %>%
  summarise(mean_stat = mean(stat))
```

```{r}
ob_stat <- msleep_dom%>%
  specify(response = is_domesticated, success = "TRUE") %>%
  calculate(stat = "prop")
```

```{r}
null_d %>%
  visualize()+
  shade_p_value(obs_stat = ob_stat, direction = "both")
```

```{r}
null_d %>%
  get_p_value(obs_stat = ob_stat, direction = "both")
```

